Synthesizing Theories of Human Language with Bayesian Program Induction

### 2018-10-17 manuscript.tex
updated data

\author
{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
\\
\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

@@

\begin{figure}
  \includegraphics[width = \textwidth]{languageComparison.png}
  \caption{Basically a placeholder -- we still need to decide exactly what to put in here and how to measure success.}\label{languageComparison}
\end{figure}

>>>>

%% \author
%% {John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
%% \\
%% \normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
%% \normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
%% \normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
%% \\
%% \normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
%% }

@@

\begin{figure}
  \includegraphics[width = \textwidth]{languageComparison.png}
  \caption{Program-synthesis-based phonological rule learner applied to 37 problems from a standard phonology textbook~\cite{9780511808869}. \% data covered by rules: fraction of the phonology problem that is explained by the learned program (so 100\% does not mean a \emph{perfect} solution, but a \emph{consistent} solution). Problems marked with an asterisk are very easy problems; the other problems are more challenging. Not shown: last dozen problems in the textbook, which are very hard.}\label{languageComparison}
\end{figure}
